Magnetised Polish doughnuts revisited

### 2017-07-10 paper_revised_v2/paper_revised_v2.tex
small typo

It is relevant to note that the only reference to the explicit form of the metric is done to show that $\mathcal{L} \neq 0$ and $\partial r \mathcal{L} \neq 0$ inside the disc. This means that our result holds for any stationary and axisymmetric metric if the aforementioned inequalities hold. Moreover, the result is also true for any angular momentum distribution that allows for the existence of a cusp and a centre (and $r_{\mathrm{c}} \neq r_{\mathrm{cusp}}$).

>>>>

It is relevant to note that the only reference to the explicit form of the metric is done to show that $\mathcal{L} \neq 0$ and $\partial_r \mathcal{L} \neq 0$ inside the disc. This means that our result holds for any stationary and axisymmetric metric if the aforementioned inequalities hold. Moreover, the result is also true for any angular momentum distribution that allows for the existence of a cusp and a centre (and $r_{\mathrm{c}} \neq r_{\mathrm{cusp}}$).
